05_DESeq_manipulation

### 2019-08-27 analysis/03_DESeq2_characterization.Rmd
move chuncks to char or manip script

>>>>

## correlation heat maps

```{r correlationheatmaps, eval = F}
plotcorrelationheatmaps(dds.female_hypothalamus, colData.female_hypothalamus ,"female hypothalamus: hatch, nest bldg., lay and day-before-hatch cluster")
plotcorrelationheatmaps(dds.female_pituitary, colData.female_pituitary, "female pituitary: clustering suggests an internal clock effect")
plotcorrelationheatmaps(dds.female_gonad, colData.female_gonad,  "female gonad: highly correlated across incubation and early nestling care")
plotcorrelationheatmaps(dds.male_hypothalamus, colData.male_hypothalamus, "male hypothalamus: 100% correlated across most parental care stages")
plotcorrelationheatmaps(dds.male_pituitary, colData.male_pituitary, "male pituitary: non-parental males are most different")
plotcorrelationheatmaps(dds.male_gondad, colData.male_gondad, "male gonad: non-parental males are most different")
```

### 2019-08-27 analysis/05_DESeq2_manipulate.Rmd
move chuncks to char or manip script

>>>>

## offspring removal

```{r offspringremoval}
g <- plotremoval(DEGs.female_hypothalamus, "Female hypothalamus", "bottom")
h <- plotremoval(DEGs.female_pituitary, "Female pituitary", "none")
i <- plotremoval(DEGs.female_gonad, "Female gonad",  "none")
j <- plotremoval(DEGs.male_hypothalamus, "Male hypothalamus", "none")
k <- plotremoval(DEGs.male_pituitary, "Male pituitary", "none")
l <- plotremoval(DEGs.male_gondad, "Male gonad", "none")

legend <- get_legend(g)

mybarplots <- plot_grid(g + theme(legend.position = "none"), h , i , j ,k , l, nrow = 2)

mybarplots2 <- plot_grid(mybarplots, legend, ncol = 1, rel_heights = c(1,0.1))
mybarplots2

pdf("../figures/sexes/offspringremoval-1.pdf", width = 10, height = 6)
plot(mybarplots2)
dev.off()

## prolong extend

```{r prolongextend}
g <- plotprolongdelay(DEGs.female_hypothalamus, "Female hypothalamus", "bottom")
h <- plotprolongdelay(DEGs.female_pituitary, "Female pituitary", "none")
i <- plotprolongdelay(DEGs.female_gonad, "Female gonad",  "none")
j <- plotprolongdelay(DEGs.male_hypothalamus, "Male hypothalamus", "none")
k <- plotprolongdelay(DEGs.male_pituitary, "Male pituitary", "none")
l <- plotprolongdelay(DEGs.male_gondad, "Male gonad", "none")

legend <- get_legend(g)

mybarplots <- plot_grid(g + theme(legend.position = "none"), h , i , j ,k , l, nrow = 2)

mybarplots2 <- plot_grid(mybarplots, legend, ncol = 1, rel_heights = c(1,0.1))
mybarplots2

pdf("../figures/sexes/prolongextend-1.pdf", width = 10, height = 6)
plot(mybarplots2)
dev.off()
